---
title: "Results on Tuesday 23rd"
author: "Théo Druilhe, Pierre Larose, Sigurd Saue and Killian Steunou"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output:
   beamer_presentation:
      fig_caption: true
      number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("kernel_barchart.R")
source("aggregate_data.R")
library(jpeg)
library(grid)
library(ggplot2)
library(dplyr)

# Load the data
data_UKR <- read.csv("data/temperature_daily_grid_UKR.csv", header = TRUE, sep = ",")
data_ESP <- read.csv("data/temperature_daily_grid_ESP.csv", header = TRUE, sep = ",")
data_POL <- read.csv("data/temperature_daily_grid_POL.csv", header = TRUE, sep = ",")
data_PRT <- read.csv("data/temperature_daily_grid_PRT.csv", header = TRUE, sep = ",")

# Convert kelvin to Celsius
data_UKR <- data_UKR %>%
  mutate_at(vars(-1:-3), ~. - 273.15)

data_ESP <- data_ESP %>%
  mutate_at(vars(-1:-3), ~. - 273.15)

data_POL <- data_POL %>%
  mutate_at(vars(-1:-3), ~. - 273.15)

data_PRT <- data_PRT %>%
  mutate_at(vars(-1:-3), ~. - 273.15)
```


# Introduction

This report presents the latest results of our work on the project. We will 
present the results of our analysis on the data we have been given, mostly through visualizations.

\tableofcontents
\newpage

# Geospatial Data Analysis

ToDo: include Theo's work on analyzing specific geographic points.

---

# Density Histograms

These plots shows the temperature densities for each year, each variable and each country.

---

<!-- Ukraine, Min -->

```{r density_histogram_ukr_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_UKR, "temperature_min", "Ukraine")
```

---

<!-- Max -->

```{r density_histogram_ukr_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_UKR, "temperature_max", "Ukraine")
```

---

<!-- Mean -->

```{r density_histogram_ukr_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_UKR, "temperature_mean", "Ukraine")
```

---

<!-- Spain, Min -->

```{r density_histogram_esp_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_ESP, "temperature_min", "Spain")
```

---

<!-- Max -->

```{r density_histogram_esp_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_ESP, "temperature_max", "Spain")
```

---

<!-- Mean -->

```{r density_histogram_esp_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_ESP, "temperature_mean", "Spain")
```

---

<!-- Poland, Min -->

```{r density_histogram_pol_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_POL, "temperature_min", "Poland")
```

---

<!-- Max -->

```{r density_histogram_pol_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_POL, "temperature_max", "Poland")
```

---

<!-- Mean -->

```{r density_histogram_pol_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_POL, "temperature_mean", "Poland")
```

---

<!-- Portugal, Min -->

```{r density_histogram_prt_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_PRT, "temperature_min", "Portugal")
```

---

<!-- Max -->

```{r density_histogram_prt_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_PRT, "temperature_max", "Portugal")
```

---

<!-- Mean -->

```{r density_histogram_prt_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_PRT, "temperature_mean", "Portugal")
```

# Linear regression

These plots shows the linear regression of the temperature variables (min, max, mean) for each country over the years.

---

<!-- ### Ukraine -->

```{r linear_regression_ukr, echo=FALSE, fig.align='center', out.width='100%'}
source("temporal_regression.R")
data_UKR_max <- read.csv("output_data/UKR/aggregate_max_UKR.csv", header = TRUE, sep = ",")
data_UKR_mean <- read.csv("output_data/UKR/aggregate_mean_UKR.csv", header = TRUE, sep = ",")
data_UKR_min <- read.csv("output_data/UKR/aggregate_min_UKR.csv", header = TRUE, sep = ",")

plot_temporal_regression(
  data_UKR_min$Median,
  data_UKR_mean$Median, 
  data_UKR_max$Median, 
  data_UKR_max$Year, 
  'Ukraine')
```

---

<!-- ### Spain -->

```{r linear_regression_esp, echo=FALSE, fig.align='center', out.width='100%'}
data_ESP_max <- read.csv("output_data/ESP/aggregate_max_ESP.csv", header = TRUE, sep = ",")
data_ESP_mean <- read.csv("output_data/ESP/aggregate_mean_ESP.csv", header = TRUE, sep = ",")
data_ESP_min <- read.csv("output_data/ESP/aggregate_min_ESP.csv", header = TRUE, sep = ",")

plot_temporal_regression(
  data_ESP_min$Median, 
  data_ESP_mean$Median, 
  data_ESP_max$Median, 
  data_ESP_max$Year, 
  'Spain')
```

---

<!-- ### Poland -->

```{r linear_regression_pol, echo=FALSE, fig.align='center', out.width='100%'}
data_POL_max <- read.csv("output_data/POL/aggregate_max_POL.csv", header = TRUE, sep = ",")
data_POL_mean <- read.csv("output_data/POL/aggregate_mean_POL.csv", header = TRUE, sep = ",")
data_POL_min <- read.csv("output_data/POL/aggregate_min_POL.csv", header = TRUE, sep = ",")

plot_temporal_regression(
  data_POL_min$Median, 
  data_POL_mean$Median, 
  data_POL_max$Median, 
  data_POL_max$Year, 
  'Poland')
```

---

<!-- ### Portugal -->

```{r linear_regression_prt, echo=FALSE, fig.align='center', out.width='100%'}
data_PRT_max <- read.csv("output_data/PRT/aggregate_max_PRT.csv", header = TRUE, sep = ",")
data_PRT_mean <- read.csv("output_data/PRT/aggregate_mean_PRT.csv", header = TRUE, sep = ",")
data_PRT_min <- read.csv("output_data/PRT/aggregate_min_PRT.csv", header = TRUE, sep = ",")
plot_temporal_regression(
  data_PRT_min$Median, 
  data_PRT_mean$Median, 
  data_PRT_max$Median, 
  data_PRT_max$Year, 
  'Portugal')
```

# Migration Analysis

ToDo

## Variable selection

ToDo

## Model Development

ToDo

# Literature Review

ToDo

# Conclusion
