---
title: "Results on Tuesday 23rd"
author: "Théo Druilhe, Pierre Larose, Sigurd Saue and Killian Steunou"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output:
   beamer_presentation:
      fig_caption: true
      number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("kernel_barchart.R")
source("aggregate_data.R")
library(jpeg)
library(grid)
library(ggplot2)
library(dplyr)

# Load the data
data_UKR <- read.csv("data/temperature_daily_grid_UKR.csv", header = TRUE, sep = ",")
data_ESP <- read.csv("data/temperature_daily_grid_ESP.csv", header = TRUE, sep = ",")
data_POL <- read.csv("data/temperature_daily_grid_POL.csv", header = TRUE, sep = ",")
data_PRT <- read.csv("data/temperature_daily_grid_PRT.csv", header = TRUE, sep = ",")

# Convert kelvin to Celsius
data_UKR <- data_UKR %>%
  mutate_at(vars(-1:-3), ~. - 273.15)

data_ESP <- data_ESP %>%
  mutate_at(vars(-1:-3), ~. - 273.15)

data_POL <- data_POL %>%
  mutate_at(vars(-1:-3), ~. - 273.15)

data_PRT <- data_PRT %>%
  mutate_at(vars(-1:-3), ~. - 273.15)
```


# Introduction

This report presents the latest results of our work on the project. We will 
present the results of our analysis on the data we have been given, mostly through visualizations.

\tableofcontents
\newpage

# Geospatial Data Analysis

ToDo: include Theo's work on analyzing specific geographic points.

---

# Density Histograms

These plots shows the temperature densities for each year, each variable and each country.
We will first look at the whole country, and then we will look at particular points.

## Country level

The next slides show 3D density histograms for each variable at the country level.

---

### Ukraine - Min

```{r density_histogram_ukr_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_UKR, "temperature_min", "Ukraine")
```

---

### Ukraine - Max

```{r density_histogram_ukr_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_UKR, "temperature_max", "Ukraine")
```

---

### Ukraine - Mean

```{r density_histogram_ukr_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_UKR, "temperature_mean", "Ukraine")
```

---

### Spain - Min

```{r density_histogram_esp_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_ESP, "temperature_min", "Spain")
```

---

### Spain - Max

```{r density_histogram_esp_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_ESP, "temperature_max", "Spain")
```

---

### Spain - Mean

```{r density_histogram_esp_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_ESP, "temperature_mean", "Spain")
```

---

### Poland - Min

```{r density_histogram_pol_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_POL, "temperature_min", "Poland")
```

---

### Poland - Max

```{r density_histogram_pol_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_POL, "temperature_max", "Poland")
```

---

### Poland - Mean

```{r density_histogram_pol_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_POL, "temperature_mean", "Poland")
```

---

### Portugal - Min

```{r density_histogram_prt_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_PRT, "temperature_min", "Portugal")
```

---

### Portugal - Max

```{r density_histogram_prt_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_PRT, "temperature_max", "Portugal")
```

---

### Portugal - Mean

```{r density_histogram_prt_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(data_PRT, "temperature_mean", "Portugal")
```

---

## Specific geographic points

The next slides show 3D density histograms for each variable at specific geographic points.

```{r get_filtered_data, include=FALSE}
source("geodetic_markers.R")
filtered_data_UKR <- filter_data_UKR(data_UKR)
filtered_data_ESP <- filter_data_ESP(data_ESP)
filtered_data_POL <- filter_data_POL(data_POL)
filtered_data_PRT <- filter_data_PRT(data_PRT)
```

---

<!-- Ukraine -->

### Ukraine

```{r ukr_map, echo=FALSE, fig.align='center', out.width='100%'}
library(mapview)
leaflet_map <- map_UKR(data_UKR)
temp_file <- tempfile(fileext = ".png")
mapshot(leaflet_map, file = temp_file)
knitr::include_graphics(temp_file)
```

---

#### South

```{r density_histogram_ukr_point_south_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_south, "temperature_min", "Ukraine - South")
```

---

```{r density_histogram_ukr_point_south_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_south, "temperature_max", "Ukraine - South")
```

---

```{r density_histogram_ukr_point_south_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_south, "temperature_mean", "Ukraine - South")
```

---

#### West

```{r density_histogram_ukr_point_west_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_west, "temperature_min", "Ukraine - West")
```

---

```{r density_histogram_ukr_point_west_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_west, "temperature_max", "Ukraine - West")
```

---

```{r density_histogram_ukr_point_west_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_west, "temperature_mean", "Ukraine - West")
```
---

#### North

```{r density_histogram_ukr_point_north_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_north, "temperature_min", "Ukraine - North")
```

---

```{r density_histogram_ukr_point_north_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_north, "temperature_max", "Ukraine - North")
```

---

```{r density_histogram_ukr_point_north_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_north, "temperature_mean", "Ukraine - North")
```

---

#### East

```{r density_histogram_ukr_point_east_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_east, "temperature_min", "Ukraine - East")
```

---

```{r density_histogram_ukr_point_east_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_east, "temperature_max", "Ukraine - East")
```

---

```{r density_histogram_ukr_point_east_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_UKR$data_UKR_east, "temperature_mean", "Ukraine - East")
```

---

### Spain

```{r density_histogram_spain_point, echo=FALSE, fig.align='center', out.width='100%'}
leaflet_map <- map_ESP(data_ESP)
temp_file <- tempfile(fileext = ".png")
mapshot(leaflet_map, file = temp_file)
knitr::include_graphics(temp_file)
```

--- 

#### North

```{r density_histogram_esp_point_north_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_north, "temperature_min", "Spain - North")
```

---

```{r density_histogram_esp_point_north_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_north, "temperature_max", "Spain - North")
```

---

```{r density_histogram_esp_point_north_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_north, "temperature_mean", "Spain - North")
```

---

#### South

```{r density_histogram_esp_point_south_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_south, "temperature_min", "Spain - South")
```

---

```{r density_histogram_esp_point_south_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_south, "temperature_max", "Spain - South")
```

---

```{r density_histogram_esp_point_south_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_south, "temperature_mean", "Spain - South")
```

---

#### Center

```{r density_histogram_esp_point_center_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_center, "temperature_min", "Spain - Center")
```

---

```{r density_histogram_esp_point_center_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_center, "temperature_max", "Spain - Center")
```

---

```{r density_histogram_esp_point_center_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_center, "temperature_mean", "Spain - Center")
```

---

#### West

```{r density_histogram_esp_point_west_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_west, "temperature_min", "Spain - West")
```

---

```{r density_histogram_esp_point_west_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_west, "temperature_max", "Spain - West")
```

---

```{r density_histogram_esp_point_west_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_ESP$data_ESP_west, "temperature_mean", "Spain - West")
```

---

### Poland

```{r density_histogram_pol_point, echo=FALSE, fig.align='center', out.width='100%'}
leaflet_map <- map_POL(data_POL)
temp_file <- tempfile(fileext = ".png")
mapshot(leaflet_map, file = temp_file)
knitr::include_graphics(temp_file)
```

---

#### North

```{r density_histogram_pol_point_north_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_POL$data_POL_north, "temperature_min", "Poland - North")
```

---

```{r density_histogram_pol_point_north_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_POL$data_POL_north, "temperature_max", "Poland - North")
```

---

```{r density_histogram_pol_point_north_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_POL$data_POL_north, "temperature_mean", "Poland - North")
```

---

#### Center

```{r density_histogram_pol_point_center_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_POL$data_POL_center, "temperature_min", "Poland - Center")
```

---

```{r density_histogram_pol_point_center_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_POL$data_POL_center, "temperature_max", "Poland - Center")
```

---

```{r density_histogram_pol_point_center_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_POL$data_POL_center, "temperature_mean", "Poland - Center")
```

---

### Portugal

```{r density_histogram_prt_point, echo=FALSE, fig.align='center', out.width='100%'}
leaflet_map <- map_PRT(data_PRT)
temp_file <- tempfile(fileext = ".png")
mapshot(leaflet_map, file = temp_file)
knitr::include_graphics(temp_file)
```

---

#### North

```{r density_histogram_prt_point_north_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_PRT$data_PRT_north, "temperature_min", "Portugal - North")
```

---

```{r density_histogram_prt_point_north_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_PRT$data_PRT_north, "temperature_max", "Portugal - North")
```

---

```{r density_histogram_prt_point_north_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_PRT$data_PRT_north, "temperature_mean", "Portugal - North")
```

---

#### West

```{r density_histogram_prt_point_west_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_PRT$data_PRT_west, "temperature_min", "Portugal - West")
```

---

```{r density_histogram_prt_point_west_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_PRT$data_PRT_west, "temperature_max", "Portugal - West")
```

---

```{r density_histogram_prt_point_west_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_PRT$data_PRT_west, "temperature_mean", "Portugal - West")
```

---

#### South

```{r density_histogram_prt_point_south_min, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_PRT$data_PRT_south, "temperature_min", "Portugal - South")
```

---

```{r density_histogram_prt_point_south_max, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_PRT$data_PRT_south, "temperature_max", "Portugal - South")
```

---

```{r density_histogram_prt_point_south_mean, echo=FALSE, fig.align='center', out.width='100%'}
plot_3d_density_by_year(filtered_data_PRT$data_PRT_south, "temperature_mean", "Portugal - South")
```

# Linear regression

These plots shows the linear regression of the temperature variables (min, max, mean) for each country over the years.

---

<!-- ### Ukraine -->

```{r linear_regression_ukr, echo=FALSE, fig.align='center', out.width='100%'}
source("temporal_regression.R")
data_UKR_max <- read.csv("output_data/UKR/aggregate_max_UKR.csv", header = TRUE, sep = ",")
data_UKR_mean <- read.csv("output_data/UKR/aggregate_mean_UKR.csv", header = TRUE, sep = ",")
data_UKR_min <- read.csv("output_data/UKR/aggregate_min_UKR.csv", header = TRUE, sep = ",")

plot_temporal_regression(
  data_UKR_min$Median,
  data_UKR_mean$Median, 
  data_UKR_max$Median, 
  data_UKR_max$Year, 
  'Ukraine')
```

---

<!-- ### Spain -->

```{r linear_regression_esp, echo=FALSE, fig.align='center', out.width='100%'}
data_ESP_max <- read.csv("output_data/ESP/aggregate_max_ESP.csv", header = TRUE, sep = ",")
data_ESP_mean <- read.csv("output_data/ESP/aggregate_mean_ESP.csv", header = TRUE, sep = ",")
data_ESP_min <- read.csv("output_data/ESP/aggregate_min_ESP.csv", header = TRUE, sep = ",")

plot_temporal_regression(
  data_ESP_min$Median, 
  data_ESP_mean$Median, 
  data_ESP_max$Median, 
  data_ESP_max$Year, 
  'Spain')
```

---

<!-- ### Poland -->

```{r linear_regression_pol, echo=FALSE, fig.align='center', out.width='100%'}
data_POL_max <- read.csv("output_data/POL/aggregate_max_POL.csv", header = TRUE, sep = ",")
data_POL_mean <- read.csv("output_data/POL/aggregate_mean_POL.csv", header = TRUE, sep = ",")
data_POL_min <- read.csv("output_data/POL/aggregate_min_POL.csv", header = TRUE, sep = ",")

plot_temporal_regression(
  data_POL_min$Median, 
  data_POL_mean$Median, 
  data_POL_max$Median, 
  data_POL_max$Year, 
  'Poland')
```

---

<!-- ### Portugal -->

```{r linear_regression_prt, echo=FALSE, fig.align='center', out.width='100%'}
data_PRT_max <- read.csv("output_data/PRT/aggregate_max_PRT.csv", header = TRUE, sep = ",")
data_PRT_mean <- read.csv("output_data/PRT/aggregate_mean_PRT.csv", header = TRUE, sep = ",")
data_PRT_min <- read.csv("output_data/PRT/aggregate_min_PRT.csv", header = TRUE, sep = ",")
plot_temporal_regression(
  data_PRT_min$Median, 
  data_PRT_mean$Median, 
  data_PRT_max$Median, 
  data_PRT_max$Year, 
  'Portugal')
```

# Migration Analysis

ToDo

## Variable selection

ToDo

## Model Development

ToDo

# Literature Review

ToDo

# Conclusion
