---
title: "Results on January 16th"
author: "Théo Druilhe, Pierre Larose, Sigurd Saue and Killian Steunou"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output:
   pdf_document:
      fig_caption: true
      number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("kernel_barchart.R")
source("aggregate_data.R")
library(jpeg)
library(grid)
library(ggplot2)
library(dplyr)

# Load the data
data_UKR <- read.csv("data/temperature_daily_grid_UKR.csv", header = TRUE, sep = ",")
data_ESP <- read.csv("data/temperature_daily_grid_ESP.csv", header = TRUE, sep = ",")
data_POL <- read.csv("data/temperature_daily_grid_POL.csv", header = TRUE, sep = ",")
data_PRT <- read.csv("data/temperature_daily_grid_PRT.csv", header = TRUE, sep = ",")

# Convert kelvin to Celsius
data_UKR <- data_UKR %>%
  mutate_at(vars(-1:-3), ~. - 273.15)

data_ESP <- data_ESP %>%
  mutate_at(vars(-1:-3), ~. - 273.15)

data_POL <- data_POL %>%
  mutate_at(vars(-1:-3), ~. - 273.15)

data_PRT <- data_PRT %>%
  mutate_at(vars(-1:-3), ~. - 273.15)
```


## Introduction
This report presents the latest results of our work on the project. We will 
present the results of our analysis on the data we have been given, mostly through visualizations.

\tableofcontents
\newpage

## Exploratory Data Analysis

### Temperature Data Analysis

We have created yearly boxplots for each country and each temperature variable.
The boxplots are presented below. The red line corresponds to the median temperature of the year 1990.

```{r boxplots, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
folders <- c("visualizations/UKR", "visualizations/ESP", "visualizations/POL", "visualizations/PRT")
filenames <- list.files(folders[1], full.names = TRUE)

display_jpg <- function(file) {
  # Read the JPEG file
  img <- readJPEG(file)
  
  # Create a new plot area
  grid.newpage()
  
  # Display the image
  grid.raster(img)
}

for (i in 1:length(folders)) {
  filenames <- list.files(folders[i], full.names = TRUE, pattern = "\\.jpg$")
  for (j in 1:length(filenames)) {
    display_jpg(file = filenames[j])
  }
}


``` 

### Geospatial Data Analysis

ToDo

## Statistical Data Analysis

### Density Histograms

These plots shows the temperature densities for each year, each variable and each country.

#### Ukraine

##### Min

```{r density_histogram_ukr_min, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_UKR, "temperature_min", "Ukraine")
```

##### Max

```{r density_histogram_ukr_max, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_UKR, "temperature_max", "Ukraine")
```

##### Mean

```{r density_histogram_ukr_mean, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_UKR, "temperature_mean", "Ukraine")
```

#### Spain

##### Min

```{r density_histogram_esp_min, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_ESP, "temperature_min", "Spain")
```

##### Max

```{r density_histogram_esp_max, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_ESP, "temperature_max", "Spain")
```

##### Mean

```{r density_histogram_esp_mean, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_ESP, "temperature_mean", "Spain")
```

#### Poland

##### Min

```{r density_histogram_pol_min, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_POL, "temperature_min", "Poland")
```

##### Max

```{r density_histogram_pol_max, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_POL, "temperature_max", "Poland")
```

##### Mean

```{r density_histogram_pol_mean, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_POL, "temperature_mean", "Poland")
```

#### Portugal

##### Min

```{r density_histogram_prt_min, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_PRT, "temperature_min", "Portugal")
```

##### Max

```{r density_histogram_prt_max, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_PRT, "temperature_max", "Portugal")
```

##### Mean

```{r density_histogram_prt_mean, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
plot_density_by_year(data_PRT, "temperature_mean", "Portugal")
```

### Linear regression

These plots shows the linear regression of the temperature variables (min, max, mean) for each country over the years.

#### Ukraine

```{r linear_regression_ukr, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
source("temporal_regression.R")
data_UKR_max <- read.csv("output_data/UKR/aggregate_max_UKR.csv", header = TRUE, sep = ",")
data_UKR_mean <- read.csv("output_data/UKR/aggregate_mean_UKR.csv", header = TRUE, sep = ",")
data_UKR_min <- read.csv("output_data/UKR/aggregate_min_UKR.csv", header = TRUE, sep = ",")

plot_temporal_regression(
  data_UKR_min$Median,
  data_UKR_mean$Median, 
  data_UKR_max$Median, 
  data_UKR_max$Year, 
  'Ukraine')
```

#### Spain

```{r linear_regression_esp, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
data_ESP_max <- read.csv("output_data/ESP/aggregate_max_ESP.csv", header = TRUE, sep = ",")
data_ESP_mean <- read.csv("output_data/ESP/aggregate_mean_ESP.csv", header = TRUE, sep = ",")
data_ESP_min <- read.csv("output_data/ESP/aggregate_min_ESP.csv", header = TRUE, sep = ",")

plot_temporal_regression(
  data_ESP_min$Median, 
  data_ESP_mean$Median, 
  data_ESP_max$Median, 
  data_ESP_max$Year, 
  'Spain')
```

#### Poland

```{r linear_regression_pol, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
data_POL_max <- read.csv("output_data/POL/aggregate_max_POL.csv", header = TRUE, sep = ",")
data_POL_mean <- read.csv("output_data/POL/aggregate_mean_POL.csv", header = TRUE, sep = ",")
data_POL_min <- read.csv("output_data/POL/aggregate_min_POL.csv", header = TRUE, sep = ",")

plot_temporal_regression(
  data_POL_min$Median, 
  data_POL_mean$Median, 
  data_POL_max$Median, 
  data_POL_max$Year, 
  'Poland')
```

#### Portugal

```{r linear_regression_prt, echo=FALSE, fig.width=12, fig.height=8, fig.align='center'}
data_PRT_max <- read.csv("output_data/PRT/aggregate_max_PRT.csv", header = TRUE, sep = ",")
data_PRT_mean <- read.csv("output_data/PRT/aggregate_mean_PRT.csv", header = TRUE, sep = ",")
data_PRT_min <- read.csv("output_data/PRT/aggregate_min_PRT.csv", header = TRUE, sep = ",")
plot_temporal_regression(
  data_PRT_min$Median, 
  data_PRT_mean$Median, 
  data_PRT_max$Median, 
  data_PRT_max$Year, 
  'Portugal')
```

## Migration Analysis

ToDo

### Variable selection

ToDo

### Model Development

ToDo

## Literature Review

ToDo

## Conclusion
